Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Add comment about dimensionality

>>>>

While the scattering coefficients have higher dimension compared to the MFCCs, this does not necessarily imply higher performance. Indeed, if the sounds to be classified were completely classified by their spectral envelopes, MFCCs would be sufficient and may even outperform the scattering transforms, since in this case the latter would contain superfluous modulation information. The results above, however, show the opposite tendency, where this additional information does in fact improve results.
